---
title: "Course Project: Shiny Application and Reproducible Pitch"
author: "Maxwell"
date: "10/11/2020"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## The application  
This application  Estimates the fuel consume  by a car, based on:

- its Weight (1000 lbs) 
- its Displacement (cu.in.) 
- its Transmission type (0 = automatic, 1 = manual) 

The user set the car data, then push the button Apply Changes

The application will calculate the estimated MPG and show a plot with other car models


## Slide with a Graph

```{r plot,  message=FALSE,warning=FALSE}
data(mtcars)
library(ggplot2)
library(plotly)

fig <- plot_ly(
  mtcars, x = ~wt, y = ~mpg,
  # Hover text:
  text = ~paste("MPG: ", mpg, 'weight:', wt),
  color = ~hp, size = ~disp
)

fig

```


## Slide with code
```{r, summary}

summary(mtcars[,1:9])

```

## Additional Information

Application:
https://maxmonteiro2008.shinyapps.io/CarMpg_Estimation/


Git repository:




